Simulations of Ballot Polling Risk-Limiting Audits

### 2022-07-19 providence/sections/workload.tex
workload progress

So for an audit $\mathcal{A}$ with expected number of ballots $E_{b}$ and expected number of rounds $E_{r}$, we get that the cost $C$ of the audit is
$$C(\mathcal{A}) = E_b * c_b + E_r * c_r.$$

@@

We let the per ballot cost be one, $c_b=1$. Then the per round cost $c_r$ tells us the cost of a round as a number of ballots. We begin with an example in which $c_r=1000$. That is, we suppose that the overhead of a round is equal to the workload of sampling $1000$ ballots.

We now consider a simple round schedule for our example. Each round is selected to give the same probability of stopping, $p$. If the audit does not stop in the first round, we find a round size which, given the sample drawn in the first round, will give a probability of stopping $p$ in the second round. For this round schedule scheme, a one-and-done audit is achieved by choosing large $p$, say $p=.9$ or $p=.95$.

The simulation results for our example are given in Figure~\ref{fig:workload}. 
For various round schedules, given by the varying parameter $p$ on the horizontal axis, we see that the average audit cost varies with a minimum at roughly $.xx$(TODO). In particular, the one-and-done $p=.9$ audits have an average of $zz\%$ higher cost than the $p=.xx$ audits.

Without extensive workload measurements, it is hard to know the most accurate value for $c_r$, and so we also evaluate the simulation results with varying $c_r$.

>>>>

So for an audit $\mathcal{A}$ with expected number of ballots $E_{b}$ and expected number of rounds $E_{r}$, we get that the cost $C$ of the audit is
\begin{equation}
C(\mathcal{A}) = E_b c_b + E_r c_r
\label{eq:cost}
\end{equation}

@@

We let the per ballot cost be one, $c_b=1$. Then the per round cost $c_r$ tells us the cost of a round as a number of ballots. We begin with an example in which $c_r=10$. That is, we suppose that the overhead of a round is equal to the workload of sampling $10$ ballots.

We now consider a simple round schedule for our example. Each round is selected to give the same probability of stopping, $p$. If the audit does not stop in the first round, we find a round size which, given the sample drawn in the first round, will give a probability of stopping $p$ in the second round. For this round schedule scheme, a one-and-done audit is achieved by choosing large $p$, say $p=.9$ or $p=.95$. For this particular round schedule scheme, computing the expected number of rounds is straightforward; . Our simulations are then used to estimate the expected number of ballots.

\begin{figure}
\includegraphics[width=.5\textwidth]{workload.png}
\caption{For cost parameters $c_b=1$ and $c_r=10$, this plot shows the expected cost for various round schedule parameters $p$. Expected cost is found using Equation~\ref{eq:cost} and the average number of ballots and rounds in our simulations as the expected number of ballots and rounds.}
\label{fig:workload}
\end{figure}

The simulation results for our example are given in Figure~\ref{fig:workload}. 
For various round schedules, given by the varying parameters $p$ on the horizontal axis, we see that the average audit cost varies with a minimum at roughly $.8$. In particular, the one-and-done $p=.9$ audits have an average of $zz\%$TODO higher cost than the $p=.8$ audits. Especially for low margin contests, using the cost-minimizing round schedule could translate to significant reduction in cost or savings in time, a particularly important factor given tight certification deadlines.

Without extensive workload measurements, it is hard to know the most accurate value for $c_r$, and so we also evaluate the simulation results with varying $c_r$. 
For each $c_r$, we find the value of $p$ which minimizes the expected workload as we did in Figure~\ref{fig:workload}. Figure~\ref{fig:optimal_ps} presents, for varying $c_r$ the round schedule parameter $p$ which minimizes expected workload.

\begin{figure}
\includegraphics[width=.5\textwidth]{optimal_ps.png}
\caption{The optimal (cost-minimizing) stopping probability $p$ for varying cost model parameters $c_r$. With $c_b=1$, the varying value of $c_r$ can equivalently be thought of as the ratio of the cost of a round to the cost of a ballot.}
\label{fig:optimal_ps}
\end{figure}
